Implications of afforestation policies for global markets

### 2023-07-07 paper.Rmd
Update paper.Rmd

>>>>

The Land Use and Land Cover Database within the GTAP framework builds upon the global land cover and land use data, incorporating forestry remote-sensing products [@baldos2012]. Using globally spatially explicit land use data, Global Trade Analysis Project Agro-Ecological Zone (GTAP-AEZ) was introduced in order to enhance the GTAP model by incorporating intra- and inter-regional land and land-based greenhouse emissions heterogeneity [@hertel2008]. It includes competition among different crops, grazing, and forest-based uses within agro-ecological zones (AEZs).

The dynamic GTAP model, supported by the GTAP-AEZ database, considers general equilibrium impacts. Land market effects, identified as significant in driving results by Stevenson et al. [@stevenson2013], are taken into account. The GTAP-AEZ database has been utilized to evaluate the impacts of crop intensification on land use, highlighting the importance of global research and development investment as a strategy to alleviate pressure on natural ecosystems. However, it is important to recognize that global aggregates may mask localized shifts that can have implications for ecologically significant areas [@byerlee2014].

Steinbuks and Hertel [@steinbuks2012] developed the FABLE model (Forestry, Agriculture, Biofuels, Land Use, and Environment) as a global partial equilibrium model to analyze optimal land use within a context of increasing demand for food, bioenergy, forest products, and non-provisioning ecosystem services, while also meeting greenhouse gas targets. The model encompasses nine sectors, including agriculture, livestock, food processing, biofuels, energy, forest, timber processing, and ecosystem services. While FABLE is a powerful tool for examining the optimal trajectory of various land uses under specific demand assumptions, it primarily focuses on specific sectors of the economy, neglecting general equilibrium effects and socio-economic or household welfare impacts [@steinbuks2012] [@hertel2017].

The KLUM@GTAP framework integrates the Kleines Land Use Model (KLUM) with an extended version of GTAP called GTAP-EFL to evaluate the impacts of climate change on cropland allocation. GTAP-EFL separates energy factors from intermediate inputs and incorporates them into capital, while also considering CO2 emissions. KLUM, a global agricultural land-use model, connects the economy to global crop allocation to maximize producer returns under specific risk assumptions. KLUM@GTAP substitutes the land allocation mechanism within GTAP-EFL by utilizing regionally aggregated area changes in cropland determined by KLUM to update cropland shares in GTAP-EFL [@ronneberger2009].
